This is the assignment for Week 2 of Course 5

1) Code for reading in the dataset and/or processing the data

```{r}
if (!file.exists("activity.csv"))
    {

    download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip", destfile = './activity.zip')
    unzip('activity.zip')
      
    }

activity_data <- read.csv("activity.csv")
activity_data$steps <- as.numeric(activity_data$steps)
activity_data$date <- as.Date(activity_data$date)
activity_data$interval <- as.numeric(activity_data$interval)

```

2) Histogram of the total number of steps taken each day

```{r}
steps_per_day <- aggregate(activity_data$steps, by = list( date = activity_data$date), FUN = mean)
names(steps_per_day) <- c('date', 'steps')
hist(steps_per_day$steps, col = 'red', main = "Histogram of total steps each day", xlab = "Total steps per day")
```

3) Mean and median number of steps taken each day

```{r}
steps_per_day_mean <- aggregate(activity_data$steps, by = list( date = activity_data$date), FUN = mean, na.rm = T)
steps_per_day_median <- aggregate(activity_data$steps, by = list( date = activity_data$date), FUN = median, na.rm = T)
merged_data <- data.frame(steps_per_day_mean$date, steps_per_day_mean$x, steps_per_day_median$x)
names(merged_data) <- c('Date', 'Mean', 'Meadian')
merged_data
```

4. Time series plot of the average number of steps taken

```{r}
library(ggplot2)
ggplot(merged_data[,1:2], aes(Date,Mean)) + geom_line()

```

5. The 5-minute interval that, on average, contains the maximum number of steps

```{r}
steps_per_interval <- aggregate(activity_data$steps, by = list( interval = activity_data$interval), FUN = mean, na.rm = T)
steps_per_interval[steps_per_interval$x == max(steps_per_interval$x),]$interval

```

6. Code to describe and show a strategy for imputing missing data

```{r}
library('imputeTS')
activity_data_imputed <- activity_data
activity_data_imputed$steps <- na.mean(activity_data_imputed$steps, option = "mean")
```

7. Histogram of the total number of steps taken each day after missing values are imputed

```{r}
steps_per_day_imputed <- aggregate(activity_data_imputed$steps, by = list( date = activity_data_imputed$date), FUN = mean)
names(steps_per_day_imputed) <- c('date', 'steps')
hist(steps_per_day_imputed$steps, col = 'red', main = "Histogram of total steps each day", xlab = "Total steps per day")
```


8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends 

```{r}
activity_data_imputed$day <- weekdays(activity_data_imputed$date)
activity_data_imputed$day_type <- ifelse(activity_data_imputed$day == "Saturday" | activity_data_imputed$day == "Sunday", "Weekend", "Weekday")
activity_data_imputed.by_interval <- aggregate(activity_data_imputed$steps, by = list( interval = activity_data_imputed$interval, day_type = activity_data_imputed$day_type), FUN = mean)

library(lattice)

xyplot(activity_data_imputed.by_interval$x ~ activity_data_imputed.by_interval$interval | factor(activity_data_imputed.by_interval$day_type), type = 'l', xlab = "Interval", ylab = "Mean number of steps")
```
